Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
removed laptop details
Documentation on the download page.

\subsection{Usability for Security Software}
\indent \indent 
We evaluate the usability of the configuration window's interface. Generally, usability 
refers to the learnability, efficiency, memorability, error rate/recoverability, and satisfaction
during use. To achieve these goals, the HCI community has established heuristics for user
interface design: visibility of the system status, using familiar
language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
error recovery, and leveraging recognition over memorization~\cite{nielsen199510}. Note
that these are not specific usability guidelines, but heuristics.

Usability has sligtly different meanings depending on the context. Some emphasize
learnability, flexibility, and ease of user. In a security context, the priorities are whatever is 
required for the security to be used effectively. As stated by Whitten \etal, a security software is 
usable if people who are expected to use it are reliably made aware of the security tasks to perform, 
are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
are sufficiently comfortable with the software interface~\cite{whitten1999johnny}. Since usable security 
has user interface design goals than general consumer software, it likewise requires usability evaluation
methods which are suitable to test these properties. Our goals are to test that the Tor Browser, 
communicates an accurate conceptual model of the task to the users as quickly as possible, provide guidance to 
users at the right time, and use warnings and other interactive tools to prevent any mistakes.

\subsection{Usability and Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

This will be the first experiment to evaluate Tor's usability as a censorship circumvention tool.
Previous work on evaluating the usability of Tor as an anonymity system have been fruitful. 
Norcie \etal identified ``stop points,'' or barriers to installing and using Tor to help streamline
the interface. Key stop points included the ability to discriminate between anonymized and non-
anonymized browser windows while using tor, unclear download and install processes, and 
confusion as to why the Tor behaves in peculiar ways~\cite{norcie2012eliminating}. A follow up
study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
effective at reducing stopping points mentioned in the previous work. The authors also present
design heuristics for designing usable anonymous systems, such as easy installation, communicating
tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees~\cite{norcie2014johnny}.

@@

We conducted the experiment on January 30-31st in Soda 
Hall at the University of Berkeley, California. We used a 2013 Macbook Air and a 
2012 Acer Aspire AS5750Z-4835 Windows laptop to give users a choice in using whatever they were comfortable with. 
All of our participants were Mac users. During the experiment, 
we recorded video data of their computer screen and audio data to capture their cognitive walkthrough. 
The average time to complete the given tasks, not including the cognitive
walkthrough nor the exit survey, was 26 minutes ($\sigma = 7$~min).

@@

As a result, Tor has developed a step-by-step visual guide on the download page to 
help Mac OS X users to bypassing the Gatekeeper during their download.

>>>>

\subsection{Usability for Security Software}
\indent \indent 
We evaluate the usability of the configuration window's interface. Generally, usability 
refers to the learnability, efficiency, memorability, error rate/recoverability, and satisfaction
during use. To achieve these goals, the computer human interaction community has established 
heuristics for user interface design: visibility of the system status, using familiar
language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
error recovery, and leveraging recognition over memorization~\cite{nielsen199510}. Note
that these are not specific usability guidelines, but heuristics.

Usability has slightly different meanings depending on the context. Some emphasize
learnability, flexibility, and ease of user. In a security context, the priorities are whatever is 
required for the security to be used effectively. As stated by Whitten \etal, a security software is 
usable if people who are expected to use it are reliably made aware of the security tasks to perform, 
are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
are sufficiently comfortable with the software interface~\cite{whitten1999johnny}. Since usable security 
has user interface design goals than general consumer software, it likewise requires usability evaluation
methods which are suitable to test these properties. Our goals are to test that the Tor Browser 
communicates an accurate conceptual model of the task to the users as quickly as possible, provides guidance to 
users at the right time, and uses warnings and other interactive tools to prevent any mistakes.

\subsection{Usability and Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective.  Clark \etal also provided guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction: Tor works may be difficult for users to understand, 
so familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

Previous work on evaluating the usability of Tor as an anonymity system have been fruitful. 
Norcie \etal identified ``stop points,'' or barriers to installing and using Tor to help streamline
the interface. Key stop points included the ability to discriminate between anonymized and non-
anonymized browser windows while using tor, unclear download and install processes, and 
confusion as to why the Tor behaves in peculiar ways~\cite{norcie2012eliminating}. A follow up
study by Norcie \etal verifies that the changes recommended to the Tor Project were indeed 
effective at reducing stopping points mentioned in the previous work. The authors also present
design heuristics for designing usable anonymous systems, such as easy installation, communicating
tradeoffs made to users, and informing why, not how, precautions are taken for security guarantees~\cite{norcie2014johnny}.

@@

We conducted the experiment on January 30-31st in Soda 
Hall at the University of Berkeley, California. We used a Mac laptop and a 
Windows laptop to give users a choice in using whatever they were comfortable with. 
All of our participants were Mac users. During the experiment, 
we recorded video data of their computer screen and audio data to capture their cognitive walkthrough. 
The average time to complete the given tasks, not including the cognitive
walkthrough nor the exit survey, was 26 minutes ($\sigma = 7$~min).

@@

When users encountered this obstacle,
they often returned to the download page, looking for hints or documentation.
The download page did not provide help for problems such as this
that are most salient immediately after downloading.
As a result, Tor has developed a step-by-step visual guide on the download page to 
help Mac OS X users to bypassing the Gatekeeper during their download.
